\documentclass[aspectratio=169]{beamer}
% 可换主题：\usetheme{metropolis}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{bookmark}

\title{Literature Review (One Page)}
\author{Chen Gao}
\date{}

\begin{document}
\begin{frame}{Literature Review (Sovereign Risk, Information, Behavior)}
\footnotesize

\textbf{Canonical quantitative sovereign default} 
[Aguiar \& Gopinath 2007; Arellano 2008; Hatchondo \& Martinez 2009; Chatterjee \& Eyigungor 2012; Mendoza \& Yue 2012] \\
\quad $\bullet$ Long-term debt with exclusion/costs; matches countercyclical spreads but struggles with \emph{persistently high premia at moderate debt}. 

\vspace{0.45em}
\textbf{Reputation / type learning as information channel}
[Cole, Dow, English 1995; Phelan 2006; Amador \& Phelan 2021, 2023; Fourakis 2024; Tomz \& Wright 2013; Mitchener \& Trebesch 2023; Morelli \& Moretti 2023] \\
\quad $\bullet$ Markets update hidden ``type'' from policy/default signals; powerful for long-run trust, but effects are typically \emph{monotone} (worse type $\Rightarrow$ uniformly worse prices).

\vspace{0.45em}
\textbf{Sunspots / market sentiment as fundamentals}
[Calvo 1996; Cole \& Kehoe 2000; Gennaioli, Martin \& Rossi 2014; Bocola \& Dovis 2019] \\
\quad $\bullet$ Expectations can self-validate crises; explains sudden stops but not necessarily \emph{systematic, state-contingent pivots} in price schedules.

\vspace{0.45em}
\textbf{Ambiguity / model uncertainty (preferences)}
[Hansen \& Sargent 2008; Pouzo \& Presno 2016; Roch \& Roldán 2023; Klibanoff, Marinacci \& Mukerji 2005; Maccheroni et al. 2006] \\
\quad $\bullet$ Worst-case tilts raise premia \emph{uniformly across states}; strong fit for high spreads, less for \emph{cross-maturity divergence} after information shocks.

\vspace{0.45em}
\textbf{Information choice / rational inattention (beliefs)}
[Sims 2003; Maćkowiak \& Wiederholt 2009; Matějka \& McKay 2015; Van Nieuwerburgh \& Veldkamp 2009; Veldkamp 2011] \\
\quad $\bullet$ Agents optimally allocate attention; allows state-dependent distortions in perceived moments (mean/variance) consistent with pricing wedges.

\vspace{0.45em}
\textbf{Diagnostic/behavioral expectations}
[Gennaioli \& Shleifer 2018; Bordalo et al. 2023; Baker \& Wurgler 2006; Gabaix 2012] \\
\quad $\bullet$ Overreaction / tail-focus can generate \emph{boom–bust}; most models imply time-varying biases rather than a \emph{time-invariant second-moment wedge}.

\vspace{0.8em}
\textbf{Steady state \& This paper: Policy-Randomness Overestimation (PRO)} \\
\quad $\bullet$ \emph{Single unified pricing operator} with PRO: lenders overweight policy dispersion $\Rightarrow$ \textbf{bond-price pivot} around a state-dependent threshold (safe states cheaper for lenders, risky states ``softening of doom''). \\
\quad $\bullet$ \textbf{Comparative statics in one operator}: higher default thresholds, \textbf{deleveraging yet higher average spreads} (\emph{stability illusion}), welfare loss from distorted intertemporal prices; operator proof of existence/uniqueness. \\
\quad $\bullet$ \textbf{RI microfoundation}: optimal attention to dispersion $\Rightarrow$ state-dependent tail weight entering the same operator, so baseline results carry over mechanically. \\
\quad $\bullet$ \textbf{Policy \& information}: limits of fiscal transfers; negativity-biased learning persistence; transparency improves welfare; event hooks (Argentina misreporting) match pivot/threshold/decoupling predictions. 
% 引用你上传的论文（按要求保留此标记）
{\scriptsize \;[Default with Policy-Randomness Overestimation] \;:contentReference[oaicite:0]{index=0}}

\vspace{0.6em}
\textbf{Empirical tension addressed} \\
\quad $\bullet$ \underline{Puzzle}: elevated, persistent premia at moderate debt (and maturity/peer \emph{decoupling}) after information shocks. \\
\quad $\bullet$ \underline{PRO vs. Reputation/Ambiguity}: reputation $\Rightarrow$ monotone price shifts; ambiguity $\Rightarrow$ uniform tilt; \textbf{PRO} $\Rightarrow$ \emph{pivot + cross-maturity divergence} and deleveraging with higher average spreads.

\end{frame}
\end{document}
